Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
blurb about nuObj

>>>>

In~\cite{nuObj}, Odersky et al. presents ${\nu}Obj$, a calculus for
classes and objects which can have types as members. It proposes three
kinds of type members: aliases, abstract types, and new types. The
calculus can encode Java's inner classes, virtual types, family
polymorphism, essential aspects of the ML-like module systems
including sharing consraints and higher-order functors, and System
$F_{<:}$~\cite{tapl}. The calculus can be used as a basis for unifying
concepts that so far existed in parallel in advanced object systems
and module systems. ${\nu}Obj$ makes the following connections: Object =
Module, Object type = Signature, Class = Method = Functor.

In terms of theoretical results, the paper confirms type soundness of
the calculus and the undecidability of type checking.
